Think deep for reef resilience

### 2025-08-17 paper/paper_draft.qmd
Further tweak to avoid ambiguous description
I avoid "this" because sometimes it becomes unclear what "this" refers to.

Carrying capacity, source-to-sink ratio and total connectivity strength and indicate that
their influence on cluster assignments is concentrated at the low range of predictor values
[@fig-ts-cluster-pdp]. This aligns with the right-skewed distributions of values across
reefs for these three predictor variables. Beyond this lower range, the partial dependence
for these reef characteristics becomes near constant, indicating that interactions with
other reef characteristics are occurring at these values which is also evidenced by their
intermediate feature importance scores.

>>>>

Analyses for carrying capacity, source-to-sink ratio and total connectivity strength
indicate that their influence on its categorical assignment is concentrated at the low range
of predictor values [@fig-ts-cluster-pdp]. This aligns with the right-skewed distributions
of values across reefs for these three predictor variables. Beyond this lower range, the
partial dependence for these reef characteristics becomes near constant, contrary to their
feature importance scores which suggest these characteristics do contribute important
information to predictions. The contrasting outcomes indicate that interactions between
other reef characteristics are driving behaviour rather than a strong influence from a
single individual characteristic.
